The language of generalization: Probability, vagueness, and interaction

### 2018-02-09 paper/comgen-paper.Rmd
cleaning first 3rd of discussion

As a formal theory of generalizations in language, we aim to unify significant swaths of language that are, on their surface, quite distinct from one another: "Birds lay eggs", "Sally smokes", "Herb X makes animals sleepy".
<!-- What these expressions have in common is *genericity*, the fact that these statements convey generalizations.  -->
We have formalized a unified, core meaning using the underlying scale of predictive probability or *prevalence*.
We showed that all three kinds of generalizations exhibit the same kind of sensitivity to context (Expt. 1, 2a \& 2b, 3).
Our framework naturally accounts for a number of logically puzzling category generalizations, or *generics* (Expt. 1).
We provide an avenue for top-down moderators on language use, by elucidating the semantic scale as defined by a subjective, predictive probability, not mere frequency (Expt. 2c).
Finally, we have shown that listeners' prior knowledge about the prevalence of the feature in a category is directly related to their endorsement of statements of genericity (Expt. 3).
<!-- In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below. -->

In this paper, we proposed a model for interpreting and endorsing generalizations in language by formalizing a simple semantic theory in a probabilistic model with structured, prior knowledge.
Our pair of models can be seen as a special case of a Rational Speech Act model, a rational framework of pragmatic language understanding [@Frank2012; @Goodman2016].
The endorsement model, which we use to generate predictions for our three case studies, is a special case of a speaker model who can only produce one of two utterances: the generalization or silence. 
The interpreter model is a "literal listener", who updates its beliefs by averaging over plausibly thresholds given prior knowledge and the simple truth-functional meaning.

<!-- The theory we present here goes beyond previous accounts in a number of useful ways. -->
<!-- The foremost contribution of our theory is that it is accompanied by a formal model, which makes precise quantitative predictions about endorsments. -->
The formal Bayesian model we articulate provides a clean separation of the semantics of a generalization from background, world knowledge.
This formal separation is a key advancement beyond previous accounts, which have either aimed to account for context-sensitivity by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [e.g., @Leslie2008].
Our model formalizes a simple semantics for generalizations and investigates the structure of world knowledge that could give rise to the context-sensitivities observed in the data.
That is, we provide a route for precise quantitative influence of conceptual structure on generic language by way of shared background knowledge between speakers and listeners [c.f., @Leslie2008].
In the rest of this discussion, we elaborate some key features of the theory that warrant future investigation, sketch out arguments for other known philosophical puzzles in genericity, and situate our theory with respect to extant theories of genericity.

@@

Our theory assumes that listeners and speakers share relevant background knowledge (in the form of a *prevalence prior*) against which generalizations are interpreted and that the language interfaces directly with *prevalence*. 
Previous psychological and philosophical work on generics has looked beyond prevalence and focused kinds and their conceptual relations to properties [@Leslie2007; @Leslie2008; @Prasada2013].
Indeed, we agree that generics are about kinds, but argue that the reason why particular generics are licensed in a context is about the information conveyed to a listener relative to their background knowledge.
This background knowledge can very well presuppose beliefs about natural kinds and assume richly structured relations between categories and the properties.
In other situations, relevant background knowledge may be merely correlational in nature.
The important commonality among such different possible domain-specific background theories is that they each have a statistical layer to them (i.e., they each give rise to beliefs about *prevalence*), which language gets to interface with.
Thus, our theory provides a clean separation between background knowledge and the semantics of generalizations; the interface between the two is predictive probability or *prevalence*.

@@

Conceptual structure including higher-order abstractions can be formalized in probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
We believe such probabilistic concept representations can be adopted as a formal analog to an intuitive theory of natural kinds [@Gelman2003; @Keil1992].
We do not assume a particular view of natural kinds in our theory, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative theory. 
Future work should investigate formalizations of attested differences in background knowledge about properties [e.g., @Prasada2013's *principled*, *statistical*, and *causal* connections] and their corresponding influence on generic endorsement.

In our modeling work, we found that empirical data that underlie the prevalence prior distributions are best modeled by a mixture-model with two mixture components.
Such a prior distribution draws qualitative distinctions (with respect to the feature) between different kinds of categories by virtue of the model representing multiple distinct components. 
It is likely that the actual conceptual knowledge against which generalizations are interpreted is far-richer than simply a two-component mixture-model.
We note, however, that a richer model of the prior is not necessary to account for the context-sensitive endorsement patterns we observe in classic philosophical cases as well as in our empirical endorsement data.

Rational models of communication, of the kind we have developed in this paper, make explicit a speaker's assumptions about the *goals of communication*, sometimes referred to as the Question Under Discussion or QUD [@roberts1996qud]. 
Our simple endorsement model assumes that the goal of communication is the prevalence.
That is, the endorsement decision is about the *prevalence* information conveyed to the listener.
This idealization will surely be elaborated in 
Richer communicative contexts will surely need to elaborate the QUD to fit more appropriately with the informational goals of the context.
We note, however, that the endorsement model makes almost identical predictions if the QUD is assumed to be about the more abstract parameters of the background knowledge (e.g., which mixture component the referent is part of).
This finding is promising for the future goal of integrating communicative goals about kinds or conceptual structure into the information-theoretic communicative framework presented here.

@@

This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
We distinguish this construct from other uses of *prevalence* in the literature, namely the usage as synonymous with frequency.
<!-- the distinction that what is communicated is probability not frequency. -->
<!-- In previous accounts, prevalence is treated as synonymous with the frequency of the feature in the category.  -->
Probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
Predictions about the presence of a feature can be the result of internal causes of the feature [e.g., in an essentialist view of natural kinds; @Gelman2003] or merely correlational happenstance.
What matters for their influence on generic endorsement, we posit, is their influence on subjective, predictive probability or *prevalence*.

@@

Communicating probabilities might seem contrary to the long attested phenomena of failures in reasoning about probability [@Tversky1974].
Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the language used to convey explicit probabilties [cf., @Levinson1995]. 
Rather than conveying *explicit probabilities*, generalizations we argue convey *implicit probabilities*, which are easier to understand and quite useful for statistical reasoning.
Given the relationship to *vague language* (described above), we argue that the utterance "70% of birds fly" is analagous to saying that "John is 6'3"", while saying "Birds fly" is more similar to saying "John is tall".
The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
Indeed, young children are actually quite good about reasoning about probabilities, but in ways that are not explicit or tied to the actual language of probability [@Gweon2010; @Dewar2010].

@@

Our model of an interpreter, or naive listener, has access to implicit statistics of the event or property in question, represented by the prior belief distribution over the prevalence $P(h)$.
The prevalence priors for a property, event, or cause are constructed by considering *other possible* categories having the property, people doing the action, or causes producing the effect.
Collectively, these other kinds, people, or causes form *comparison classes* against which the referent-category is evaluated.
Thus, the prevalence prior $P(h)$ is constructed with respect some comparison class $C$: $P_C(h)$.

The existence of comparison classes is uncontroversial in the study of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analagous to the context-sensitivity of the language of generalizations explored in this paper.
However, like the semantics of generalizations, the other entities or categories that comprise the comparison class are underspecified.

Uncertainty about the comparison class adds yet more flexibility to generalizations.
Even if interlocutors coordinate on a particular comparison class (e.g., agreeing that they are talking *relative to other animals*), they may disagree about the prevalences for other *other categories* in the class.
That is, our model makes the prediction that the acceptance or rejection of the statement "Humans cause global warming" or "Muslims are terrorists" depends upon a speaker's beliefs about how other forces (e.g., plate tectonics) influence the climate or how often other categories (e.g., neo-nazis) commit acts of terrorism.
In Expt. 3, we demonstrated the influence of other categories on endorsement of a generalization.
Understanding how knowledge of the comparison class influences language use is an exciting new area for future research in the language of generalizations.

Interlocturs may not only fail to coordinate on what categories are in the comparison class, the prevalences that may be assumed for the constituent categories of the comparison class, but *how* the comparison class should be constructed.
The comparison classes used in our case studies were with respect to the target *category* (*other animals*, *other people*, *other possible causes*); thus, our model addresses the implicit Question Under Discussion [QUD; @roberts1996qud] of "*what* has feature?".
Were the QUD to be reversed (e.g., "what features does category have?"), the comparison classes would need to be constructed with respect to the *feature* (e.g., *other features*, *other actions*, *other effects*).
The same sentence can be used to address multiple QUDs [@KrifkaGenericBookFocus], giving rise to multiple distinct comparison classes.
The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law."; imagine in a pedagogical context) or a feature-wise comparison class (i.e., "Lawyers care about the law *(as opposed to justice, doing what's morally right, ...)*" e.g., when said sardonically).
In this work, we focused on category-wise comparison classes for methodological convenience.
Future work should investigate the factors that give rise to feature-wise interpretations of generalizations, and how the relevant comparison classes are constructed.

@@

Perhaps the most surprising aspect of the language of generalization is how difficult it is to formalize, given how common they are in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004].
<!-- from a formal perspective is that generic language is far from trivial to characterize.  -->
<!-- Generalizations are common in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004], -->
Generalizations are often contrasted with quantifier language (e.g., "some", "most", "all", ...), which is in fact *easier* to formalize, but more difficult for young children to acquire [@Brandone2014; @Gelman2015].
<!-- If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...). -->
<!-- The extreme flexibility of generic meaning (e.g., "Birds lay eggs" vs. "Birds are female") stands in stark contrast to its early emergence in development. -->
<!-- In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015], and are often confused for generic statements [@Leslie2012a]. -->
This asymmetry between the simplicity of the formal theory and the age acquisition has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is inapprorpriate for generic language [@Leslie2008].

Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater.
The acquisition of a threshold-based truth-functional meaning $\denote{u}(h, \theta) = \{h :h > \theta\}$ requires learning at least three aspects of meaning: 
(1) the *dimension* being described (i.e., the probability $h$),
(2) the *polarity* of the relation (i.e., $>$ vs. $<$), and 
(3) the value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
Upon acquiring the dimension and the polarity, a rational learner should represent uncertainty over possible thresholds $\theta$.
Upon repeated cross-situational data, this prior could be updated towards acquiring a fixed meaning.
However, for generalizations, no fixed threshold is required; the language of generalization is acquired once aspects (1) and (2) are learned.
<!-- In our model, $\theta$ is left underspecified in the semantics and is inferred in context. -->
This informal analysis predicts that a child would first acquire generalizations, and from that, carve out more precise meanings for quantified language, consistent with the developmental data.

There is a secondary argument for why the semantics we posit presents an easy learning problem.
<!-- The uniform prior over the threshold $\theta$ in the truth-functional semantics (as we have assumed in our model) provides a secondary argument for why acquiring our semantics for generics should be easy. -->
Uniform uncertainty over values in the unit interval $[0, 1]$ for threshold $\theta$ in a threshold-function (as we have assumed in our model) is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the degree, in this prevalence $h$ itself: $\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h$
This *soft semantics* (corresponding intuitively to a meaning like "the higher the probability, the better", or simply "more is better") is perhaps the simplest quantitative semantics one could posit.
The difficulty in acquiring the meaning of quantifiers is then a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
We leave for future work the precise implementation of the acquisition model we sketch out here.

>>>>

As a formal theory of the language of generalization, our framework aims to unify large swaths of language that are, on their surface, quite distinct from one another: "Birds lay eggs", "Sally smokes", "Herb X makes animals sleepy".
<!-- What these expressions have in common is not surface features but generalization (also referred to as *genericity*). -->
We have formalized a unified, core meaning of generalization in language using the underlying scale of predictive probability or *prevalence*.
We showed that endorsements of all three types of generalizations exhibit the same sensitivity to a background distribution comprised of other categories (Expt. 1, 2a \& 2b, 3).
As well, our framework naturally accounts for a number of logically puzzling category generalizations (Expt. 1) and provides an avenue for top-down moderators on language use, by elucidating the semantic scale as defined by a subjective, predictive probability, not mere frequency (Expt. 2c).
Finally, we have shown that listeners' prior knowledge about the prevalence of the feature in a category is directly related to their endorsement of statements of genericity (Expt. 3).
<!-- In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below. -->

In this paper, we proposed a model for interpreting and endorsing generalizations in language by formalizing a simple semantic theory in a communicative model with shared background knowledge.
Our pair of models can be seen as a special case of a Rational Speech Act model, a rational framework of pragmatic language understanding [@Frank2012; @Goodman2016].
The endorsement model, which we use to generate predictions for our three case studies, is a special case of a speaker model who can only produce one of two utterances: the generalization or silence. 
The interpreter model is a "literal listener", who updates its beliefs by averaging over plausibly thresholds given prior knowledge and the simple truth-functional meaning.

<!-- The theory we present here goes beyond previous accounts in a number of useful ways. -->
<!-- The foremost contribution of our theory is that it is accompanied by a formal model, which makes precise quantitative predictions about endorsments. -->
The formal Bayesian model we articulate provides a clean separation of the semantics of a generalization from background, world knowledge.
This formal separation is a key advancement beyond previous accounts, which have either aimed to account for context-sensitivity by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [e.g., @Leslie2008].
Our model formalizes a simple meaning for generalizations and investigates the structure of world knowledge that could give rise to the context-sensitivities observed in the data.
That is, we provide a route for precise quantitative influence of conceptual knowledge on generic language by way of shared background knowledge between speakers and listeners.
In the rest of this discussion, we elaborate some key features of the theory that warrant further investigation, sketch out arguments for other known philosophical puzzles in genericity, and situate our theory with respect to extant theories of genericity.

@@

Our theory assumes that listeners and speakers share relevant background knowledge (in the form of a *prevalence prior*) against which generalizations are interpreted.
Given this representation of background knowledge (*prevalence prior*), language interfaces with conceptual knowledge via *prevalence*. 
Previous psychological and philosophical work on generics has looked beyond prevalence and focused kinds and their conceptual relations to properties [@Leslie2007; @Leslie2008; @Prasada2013].
Indeed, we see generics as describing kinds, but argue that the reason why particular generics are licensed in a context is about the information conveyed to a listener relative to their background knowledge, formalized with by prevalence prior.
In the right situations, this shared background knowledge can presuppose beliefs about natural kinds and assume richly structured relations between categories and the properties [a la @Prasada2013].
In other situations, relevant background knowledge may be merely correlational in nature.

Conceptual structure including higher-order abstractions can be formalized in probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
We believe such probabilistic concept representations can be adopted as a formal analog to an intuitive theory of natural kinds [@Gelman2003; @Keil1992].
We do not assume a particular view of natural kinds in our model, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative theory. 
The important commonality among different domain-specific background theories is that they each have a statistical layer to them (i.e., they each give rise to beliefs about *prevalence*), which language interfaces with via the tools of truth-functional semantics.
Thus, our theory provides a separation between background knowledge and the semantics of generalizations; the interface between the two is predictive probability or *prevalence*. 
Future work should investigate formalizations of attested differences in background knowledge about properties [e.g., @Prasada2013's *principled*, *statistical*, and *causal* connections] and their corresponding influence on generic endorsement via prevalence priors.

@@

In our modeling work, we found that the empirical data which underlie the prevalence prior distributions are best modeled by a mixture-model with two mixture components.
Such a prior distribution draws qualitative distinctions between different kinds of categories by virtue of the prevalence prior model representing multiple distinct components. 
Actual conceptual knowledge against which generalizations are interpreted is most likely far-richer than simply a two-component mixture-model.
We note, however, that a richer model of the prior is not necessary to account for the context-sensitive endorsement patterns we observe in our empirical data.

The rational model of communication that we have developed in this paper makes explicit a speaker's assumptions about the goals of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud]. 
Our simple endorsement model assumes that the goal of communication is the prevalence (Eq.\ref{eq:S1}).
In other words, the endorsement decision is computed with respect to the prevalence information conveyed to the listener.
Richer communicative contexts will surely need to elaborate the QUD to fit more appropriately with the informational goals of the context in which generalizations are produced.
We note, however, that the endorsement model makes almost identical predictions if the QUD in the model is assumed to be about the abstract parameters of the background knowledge (e.g., which mixture component the referent is part of).
This observation is promising for the future goal of integrating communicative goals about kinds or conceptual structure into the information-theoretic communicative framework presented here.

@@

This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
We distinguish this construct from other uses of *prevalence* in the literature, namely the usage as synonymous with frequency.
<!-- the distinction that what is communicated is probability not frequency. -->
<!-- In previous accounts, prevalence is treated as synonymous with the frequency of the feature in the category.  -->
Probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
Predictions about the presence of a feature can be the result of beliefs about internal causes of the feature [e.g., in an essentialist view of natural kinds; @Gelman2003] or merely correlational happenstance.
What matters for their influence on generic endorsement, however, is their influence on subjective, predictive probability or *prevalence*.

@@

Communicating probabilities might seem contrary to the long attested failures in reasoning about probability [@Tversky1974].
Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the language used to convey explicit probabilties [cf., @Levinson1995]. 
Rather than conveying *explicit probabilities*, generalizations we argue convey *implicit probabilities*.
In other words, we argue that the utterance "70% of birds fly" is a precise statement about how many birds fly in the way that "John is 6'3"" is a precise statement about the height of John, whereas "Birds fly" is a vague statement more akin to utterance "John is tall".
The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
Indeed, young children are actually quite good with reasoning about probabilities, but in ways that are not explicit or tied to the actual language of probability [@Xu2008; @xu2009statistical].

@@

The probabilistic communicative model we introduce in this paper assumes shared background 
<!-- Our model of an interpreter, or naive listener, has access to implicit  -->
statistics of the event or property in question, represented by the prior belief distribution over the prevalence $P(h)$.
We constructed prevalence priors for a property, event, or cause by considering *other possible* categories having the property, people doing the action, or causes producing the effect.
Collectively, these other kinds, people, or causes form *comparison classes* against which the referent-category is evaluated.
Thus, the prevalence prior $P(h)$ is actually a conditional distribution constructed with respect some comparison class $C$: $P(h \mid C)$.

The existence of comparison classes is uncontroversial in the study of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analagous to the context-sensitivity of the language of generalizations explored in this paper.
An important problem for comparison classes for both gradable adjectives and generalizations is that the comparison class often goes unsaid (e.g., "John is tall for a person" is often produced as just "John is tall").

Uncertainty about the comparison class adds yet more opportunity for miscommunication, deceit, or just faultless disagreement to the language of generalization.
Even if interlocutors roughly coordinate on a particular comparison class (e.g., agreeing that they are talking *relative to other animals*), they may disagree about the prevalences for other categories in the comparison class.
That is, our model makes the prediction that the acceptance or rejection of controversial statements (e.g., "Muslims are terrorists") depends upon a speaker's beliefs about how often other categories exhibit the property (e.g., neo-nazis commiting acts of terrorism).
In Expt. 3, we empirically demonstrated the influence of other categories on endorsement of a generalization.
Understanding how knowledge of the comparison class influences language use is an exciting new area for future research in the language of generalizations.

Finally, interlocturs may not only fail to coordinate on what categories are in the comparison class, the prevalences that may be assumed for the constituent categories of the comparison class, but the very nature of *how* the comparison class should be constructed.
The comparison classes used in our case studies were with always respect to the *category* (*other animals*, *other people*, *other possible causes*); thus, our model addresses the implicit QUD of "*what* has feature?".
Were the QUD to be reversed (e.g., "what features does the category have?"), the comparison classes would be constructed with respect to the *feature* (e.g., *other features*, *other actions*, *other effects*).
It's long been noted that the same generalization can be used to address multiple QUDs [@KrifkaGenericBookFocus], and we posit that differences in interpretation are the result of multiple distinct comparison classes competing for influence.
The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law."; imagine in a pedagogical context) or a feature-wise comparison class (i.e., "Lawyers care about the law *(as opposed to justice, doing what's morally right, ...)*" e.g., when said sardonically).
In this work, we focused on category-wise comparison classes purely for methodological convenience.
Future work should investigate the factors that give rise to feature-wise interpretations of generalizations, and how the relevant comparison classes are constructed.

@@

Perhaps the most surprising aspect of the language of generalization is how difficult it is to formalize, given how common it is in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004].
<!-- from a formal perspective is that generic language is far from trivial to characterize.  -->
<!-- Generalizations are common in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004], -->
Generalizations are often contrasted with quantifier language (e.g., "some", "most", "all", ...), which is in fact *easier* to formalize, but more difficult for young children to acquire [@Brandone2014; @Gelman2015].
<!-- If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...). -->
<!-- The extreme flexibility of generic meaning (e.g., "Birds lay eggs" vs. "Birds are female") stands in stark contrast to its early emergence in development. -->
<!-- In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015], and are often confused for generic statements [@Leslie2012a]. -->
This asymmetry between the simplicity of the formal theory and the age of acquisition has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is inapprorpriate for generalizations  [@Leslie2008].

Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater.
The acquisition of a threshold-based truth-functional meaning $\denote{u}(h, \theta) = \{h :h > \theta\}$ requires learning at least three distinct aspects of meaning: 
(1) the *dimension* being described (i.e., probability $h$),
(2) the *polarity* of the relation (i.e., $>$ vs. $<$), and 
(3) the value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
Upon acquiring the dimension and the polarity, a rational learner should represent uncertainty over possible thresholds $\theta$.
Upon repeated cross-situational data, this prior could be updated towards acquiring a fixed meaning.
However, for generalizations, no fixed threshold is required; the language of generalization is learned once aspects (1) and (2) are understood.
<!-- In our model, $\theta$ is left underspecified in the semantics and is inferred in context. -->
This informal analysis predicts that a child would first acquire the language of generalizations, and from that, carve out more precise meanings for quantified language, consistent with the developmental data.

There is a secondary argument for why our semantics presents an easy learning problem.
<!-- The uniform prior over the threshold $\theta$ in the truth-functional semantics (as we have assumed in our model) provides a secondary argument for why acquiring our semantics for generics should be easy. -->
Uniform uncertainty over values in the unit interval $[0, 1]$ for threshold $\theta$ in a threshold-function (as we have assumed in our model) is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the degree itself, in this case prevalence $h$: $\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h$
This *soft semantics* (corresponding intuitively to a meaning like "the higher the probability, the better", or simply "more is better") is perhaps the simplest quantitative semantics one could posit.
The difficulty in acquiring the meaning of quantifiers is then a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
We leave for future work the precise implementation of the acquisition model we sketch out here.
